Markov Chain Monte Carlo (MCMC)

### 2016-04-21 articles/articles.Rmd
bayes done for now

---
title: "Articles"
author: "Ming-Yu Liu"
output: 
  html_document: 
    highlight: haddock
    toc: yes
---

@@

- Doing Data Science Right — Your Most Common Questions Answered. [[Review](http://firstround.com/review/doing-data-science-right-your-most-common-questions-answered/?imm_mid=0e29cf&cmp=em-data-na-na-newsltr_20160413)]
- Principles of good data analytics. [[blog](http://www.gregreda.com/2014/03/23/principles-of-good-data-analysis/)] 
- Why I Ditched My Fitbit and What This Means for Analytics. [[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/why-i-ditched-my-fitbit-and-what-this-means-for-analytics)]
- Know the Difference between Customer Service and Customer Experience. [[Harvard Business Review](https://hbr.org/sponsored/2016/03/know-the-difference-between-customer-service-and-customer-experience?utm_source=twitter&utm_medium=social&utm_campaign=harvardbiz)]
- Two articles about saying no to p-values. [[R-bloggers](http://www.r-bloggers.com/after-150-years-the-asa-says-no-to-p-values/)][[R-bloggers](http://www.r-bloggers.com/its-not-the-p-values-fault-reflections-on-the-recent-asa-statement-relevant-r-resources/)]
- The 9 Best Marketing And Sales Analytics You Should Know About.[[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/the-9-best-marketing-and-sales-analytics-you-should-know-about)]
- Cohort analysis. [[Youtube](https://www.youtube.com/watch?v=NyhVdGmnh0I)]
- Ted Talk : How to use data to make a hit TV show. [[Ted](http://www.ted.com/talks/sebastian_wernicke_how_to_use_data_to_make_a_hit_tv_show?utm_campaign=social&utm_medium=referral&utm_source=facebook.com&utm_content=talk&utm_term=technology)]

>>>>

---
title: "Articles"
date: "`r Sys.Date()`"
author: "Ming-Yu Liu"
output:
  rmdformats::readthedown:
    highlight: pygments
---

@@

- Using Machine Learning to Predict Customer Behaviour [[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/using-machine-learning-to-predict-customer-behaviour)]
    - Used with Complaints Management, Customer Upsell and Customer Retention. Questions include How to anticipate and manage the dissatisfaction of the customers?', 'How to sell more and better to existing customers?' and 'How to keep the most profitable customers at an appropriate cost?'
    - Action: You identify a target behaviour, in our case, it is a specific customer action, like filing a complaint/not filing a complaint, accepting or rejecting an upsell offer, cancelling / not cancelling a service. Then perform supervised learning
- Doing Data Science Right — Your Most Common Questions Answered. [[Review](http://firstround.com/review/doing-data-science-right-your-most-common-questions-answered/?imm_mid=0e29cf&cmp=em-data-na-na-newsltr_20160413)]
- Principles of good data analytics. [[blog](http://www.gregreda.com/2014/03/23/principles-of-good-data-analysis/)] 
- Why I Ditched My Fitbit and What This Means for Analytics. [[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/why-i-ditched-my-fitbit-and-what-this-means-for-analytics)]
- Know the Difference between Customer Service and Customer Experience. [[Harvard Business Review](https://hbr.org/sponsored/2016/03/know-the-difference-between-customer-service-and-customer-experience?utm_source=twitter&utm_medium=social&utm_campaign=harvardbiz)]
- Two articles about saying no to p-values. [[R-bloggers](http://www.r-bloggers.com/after-150-years-the-asa-says-no-to-p-values/)][[R-bloggers](http://www.r-bloggers.com/its-not-the-p-values-fault-reflections-on-the-recent-asa-statement-relevant-r-resources/)]
- The 9 Best Marketing And Sales Analytics You Should Know About.[[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/the-9-best-marketing-and-sales-analytics-you-should-know-about)]
- Cohort analysis. [[Youtube](https://www.youtube.com/watch?v=NyhVdGmnh0I)]
- Ted Talk : How to use data to make a hit TV show. [[Ted](http://www.ted.com/talks/sebastian_wernicke_how_to_use_data_to_make_a_hit_tv_show?utm_campaign=social&utm_medium=referral&utm_source=facebook.com&utm_content=talk&utm_term=technology)]

### 2016-04-21 bayesian_statistics/MCMC/MCMC.Rmd
bayes done for now

*Markov Chain Monte Carlo (MCMC)* is a class of methods in which we can simulate draws (taking samples) that are slightly dependent and are approximately from a (posterior) distribution. We then take those draws and calculate quantities of interest for the (posterior) distribution. In Bayesian statistics, there are generally two MCMC algorithms that we use: the **Gibbs Sampler** and the **Metropolis-Hastings algorithm**.

@@

## Markov Chain Monte Carlo (MCMC)

@@

When we setup a Bayesian inference problem with N unknowns, we are implicitly creating an N dimensional space for the **prior distributions** to exist in. Associated with the space is an additional dimension, which we can describe as the surface, or curve, that sits on top of the space, that reflects the **prior probability** of a particular point. The plots above visualize this. The more blue the color, the more **prior probability** is assigned to that location. Conversely, areas with whiter color represent that our priors assign very low probability to that location.

@@

## Gibbs Sampling

The MCMC method we've introduced above is also known as the *Metropolis-Hastings algorithm*. It is very general and broadly applicable, but one drawback is that your proposed distribution has to be properly tuned to the posterior distribution. Recall that we proposed a new random sample point using the a normal distribtuion with the mean of 1 and standard deviation of 1 `rnorm( ..., mean = 0, sd = 1 )`. If this random sample point generator's distribution is too wide or too narrow, a large proportion of our proposed sample point will still be rejected. Or more intuitively, the effectiveness of our random walk will farely low.

Given this situation, there's an alternative sampling algorithm called **Gibbs Samplinig**. Unlike the **Metropolis Sampling**, with **Gibbs Samplinig**  all proposed jumps are accepted.

## Takeaways

- If you can decompose your probability distribution into conditional probabilities, then **Gibbs Samplinig** is preferable over **Metropolis Sampling**.

>>>>

*Markov Chain Monte Carlo (MCMC)* is a class of methods in which we can simulate draws (taking samples) that are slightly dependent and are approximately from a (posterior) distribution. We then take those draws and calculate quantities of interest for the (posterior) distribution. Here, we'll bw attempting to give you an intuition behind one branch of the MCMC sampling, namely the **Metropolis–Hastings Algorithm**.

@@

## MCMC - Metropolis–Hastings Algorithm

@@

@@
